Modeling Ionic Polymer-Metal Composites\\ with Space-Time Adaptive Multimesh \emph{hp}-FEM

### 2011-03-22 pugal-cicp2010.tex
Submitted final version

\bibliographystyle{amsrn}    % Bibliography: Author-Date system
\bibliography{pugal-esco2010}      % pls. call your database here

>>>>

\bibliographystyle{amsrn}    % Bibliography: Author-Date system
%\bibliography{pugal-cicp2010}      % pls. call your database here
\begin{bibdiv}
\begin{biblist}

\bib{basu1997membrane}{article}{
      author={Basu, S.},
      author={Sharma, M.M.},
       title={{An improved space-charge model for flow through charged
  microporous membranes}},
        date={1997},
     journal={Journal of Membrane Science},
      volume={124},
      number={1},
       pages={77\ndash 91},
}

\bib{bazant2004diffuse}{article}{
      author={Bazant, M.Z.},
      author={Thornton, K.},
      author={Ajdari, A.},
       title={{Diffuse-charge dynamics in electrochemical systems}},
        date={2004},
        ISSN={1550-2376},
     journal={Physical Review E},
      volume={70},
      number={2},
       pages={21506},
}

\bib{dubcova2010space}{article}{
      author={Dubcova, L.},
      author={Solin, P.},
      author={Cerveny, J.},
      author={Kus, P.},
       title={{Space and Time Adaptive Two-Mesh $hp$-Finite Element Method for
  Transient Microwave Heating Problems}},
        date={2010},
     journal={Electromagnetics},
      volume={30},
      number={1},
       pages={23\ndash 40},
}

\bib{nasser2002applied}{article}{
      author={Nemat-Nasser, S.},
       title={Micromechanics of actuation of ionic polymer-metal composites},
        date={2002},
     journal={Journal of Applied Physics},
      volume={92},
      number={5},
       pages={2899\ndash 2915},
}

\bib{newbury2003intelligent}{article}{
      author={Newbury, K.M.},
      author={Leo, D.J.},
       title={{Linear electromechanical model of ionic polymer transducers-Part
  I: Model Development}},
        date={2003},
     journal={Journal of Intelligent Material Systems and Structures},
      volume={14},
      number={6},
       pages={333},
}

\bib{pugal2009}{inproceedings}{
      author={Pugal, D.},
      author={Aabloo, A.},
      author={Kim, K.~J.},
       title={Dynamic surface resistance model of ipmc},
        date={2009},
      editor={Ounaies, Zoubeida},
      editor={Li, Jiangyu},
      volume={7289},
   publisher={SPIE},
       pages={72891E},
}

\bib{pugal2010polymer}{article}{
      author={Pugal, D.},
      author={Jung, K.},
      author={Aabloo, A.},
      author={Kim, K.J.},
       title={{Ionic polymer-metal composite mechanoelectrical transduction:
  review and perspectives}},
        date={2010},
     journal={Polymer international},
      volume={59},
      number={3},
       pages={279\ndash 289},
}

\bib{pugal2010spie3d}{inproceedings}{
      author={Pugal, D.},
      author={Kim, K.~J.},
      author={Aabloo, A.},
       title={Modeling the transduction of ipmc in 3d configurations},
        date={2010},
      editor={Ounaies, Zoubeida},
      editor={Li, Jiangyu},
      volume={7644},
   publisher={SPIE},
       pages={76441T},
}

\bib{pugal2008appliedphysics}{article}{
      author={Pugal, D.},
      author={Kim, K.~J.},
      author={Punning, A.},
      author={Kasemagi, H.},
      author={Kruusmaa, M.},
      author={Aabloo, A.},
       title={A self-oscillating ionic polymer-metal composite bending
  actuator},
        date={2008},
     journal={Journal of Applied Physics},
      volume={103},
      number={8},
       pages={084908},
}

\bib{shahinpoor2001smartmat}{article}{
      author={Shahinpoor, M.},
      author={Kim, K.~J.},
       title={Ionic polymer-metal composites: I. fundamentals},
        date={2001},
     journal={Smart Materials and Structures},
      volume={10},
      number={4},
       pages={819},
}

\bib{solin2010pde}{article}{
      author={Solin, P.},
      author={Andrs, D.},
      author={Cerveny, J.},
      author={Simko, M.},
       title={{PDE-independent adaptive $hp$-FEM based on hierarchic extension
  of finite element spaces}},
        date={2010},
     journal={Journal of computational and applied mathematics},
      volume={233},
      number={12},
       pages={3086\ndash 3094},
}

\bib{solin2010monolithic}{article}{
      author={Solin, P.},
      author={Cerveny, J.},
      author={Dubcova, L.},
      author={Andrs, D.},
       title={{Monolithic discretization of linear thermoelasticity problems
  via adaptive multimesh hp-FEM}},
        date={2010},
     journal={Journal of computational and applied mathematics},
      volume={234},
      number={7},
       pages={2350\ndash 2357},
}

\bib{solini2010adaptive}{article}{
      author={Solin, P.},
      author={Dubcova, L.},
      author={Dolezel, I.},
       title={{Adaptive $hp$-FEM with arbitrary-level hanging nodes for
  Maxwell’s equations}},
        date={2010},
     journal={Advances in Applied Mathematics and Mechanics},
      volume={2},
      number={4},
       pages={518\ndash 532},
}

\bib{solin2010adaptive}{article}{
      author={Solin, P.},
      author={Dubcova, L.},
      author={Kruis, J.},
       title={{Adaptive $hp$-FEM with dynamical meshes for transient heat and
  moisture transfer problems}},
        date={2010},
     journal={Journal of computational and applied mathematics},
      volume={233},
      number={12},
       pages={3103\ndash 3112},
}

\bib{Hermes-book}{book}{
      author={Solin, P.},
      author={Segeth, K.},
      author={Dolezel, I.},
       title={Higher-order finite element methods},
   publisher={Chapman \& Hall / CRC Press},
        date={2003},
}

\bib{valli2002control}{article}{
      author={Valli, A. M.~P.},
      author={Carey, G.~F.},
      author={Coutinho, A.},
       title={{Control strategies for timestep selection in simulation of
  coupled viscous flow and heat transfer}},
        date={2002},
     journal={Communications in Numerical Methods in Engineering},
      volume={18},
      number={2},
       pages={131\ndash 139},
}

\bib{wallmersperger2007appliedphysics}{article}{
      author={Wallmersperger, T.},
      author={Leo, D.~J.},
      author={Kothera, C.~S.},
       title={Transport modeling in ionomeric polymer transducers and its
  relationship to electromechanical coupling},
        date={2007},
     journal={Journal of Applied Physics},
      volume={101},
      number={2},
       pages={024912},
}

\end{biblist}
\end{bibdiv}
